AMEN tutorial

### 2020-03-06 code/reiter_stam_2003/amen-tutorial.Rmd
CD RMD code review

---
title: "AMEN tutorial"
author: "Juan Tellez"
date: "2/27/2020"
output:
  pdf_document: default
  html_document: default
---

@@

```{r load-amen, eval=FALSE}
## load most updated amen package
devtools::install_github('s7minhas/amen') ; library(amen)

@@

```{r load-posterior, eval=FALSE}
## load model fits from 0 to 3 dimensions
load( paste0(resultsPath,'ameFit_k0.rda') ) ; ameFit_k0=ameFit
# load( paste0(resultsPath,'ameFit_k1.rda') ) ; ameFit_k1=ameFit
# load( paste0(resultsPath,'ameFit_k2.rda') ) ; ameFit_k2=ameFit
# load( paste0(resultsPath,'ameFit_k3.rda') ) ; ameFit_k3=ameFit
```

@@

```{r amen-gof, eval=FALSE}
## check out goodness of fit stats in posterior estimate for each dimension
amen::gofPlot(ameFit_k0$GOF, symmetric = TRUE)
```

@@

```{r beta-params, eval=FALSE}
## check out beta parameters (posterior estimates for coefficients) 
## and convergence for each dimension
summStats = function(x){
  # credible intervals
  res=c(mu=mean(x),med=median(x),sd=sd(x),quantile(x,probs=c(0.025,0.05,0.95,0.975))) 
  round(res, 3)
}
apply(ameFit_k0$BETA, 2, summStats) %>% t() %>% nrow()
```

@@

```{r beta-converge, eval=FALSE}
betaIndices<-split(1:ncol(ameFit_k0$BETA), ceiling(seq_along(1:ncol(ameFit_k0$BETA))/5))
```

@@

```{r plot-converge, eval=FALSE}
## plot the parameters convergence using dimension k=0
for(bIndex in betaIndices){ amen::paramPlot( ameFit_k0$BETA[,bIndex,drop=FALSE] ) }
amen::paramPlot(ameFit_k0$VC)
```

>>>>

---
title: "AMEN tutorial"
author: "Juan Tellez"
date: "2/27/2020"
output:
  html_document: default
  pdf_document: default
---

@@

```{r load-amen, eval=TRUE}
## load most updated amen package
devtools::install_github('s7minhas/amen') ; library(amen)

@@

```{r load-posterior, eval=TRUE}
## load model fits from 0 to 3 dimensions
load( paste0(resultsPath,'model_k0_v12.rda') ) ; ameFit_k0=ameFit
# load( paste0(resultsPath,'model_k1_v12.rda') ) ; ameFit_k1=ameFit
# load( paste0(resultsPath,'model_k2_v12.rda') ) ; ameFit_k2=ameFit
# load( paste0(resultsPath,'model_k3_v12.rda') ) ; ameFit_k3=ameFit
```

@@

```{r amen-gof, eval=TRUE}
## check out goodness of fit stats in posterior estimate for each dimension
amen::gofPlot(ameFit_k0$GOF, symmetric = TRUE)
```

@@

```{r beta-params, eval=TRUE}
## check out beta parameters (posterior estimates for coefficients) 
## and convergence for each dimension
summStats = function(x){
  # credible intervals
  res=c(mu=mean(x),med=median(x),sd=sd(x),quantile(x,probs=c(0.025,0.05,0.95,0.975))) 
  round(res, 3)
}
apply(ameFit_k0$BETA, 2, summStats) %>% t() 
```

@@

```{r beta-converge, eval=TRUE}
betaIndices<-split(1:ncol(ameFit_k0$BETA), ceiling(seq_along(1:ncol(ameFit_k0$BETA))/5))
```

@@

```{r plot-converge, eval=TRUE}
## plot the parameters convergence using dimension k=0
for(bIndex in betaIndices){ amen::paramPlot( ameFit_k0$BETA[,bIndex,drop=FALSE] ) }
amen::paramPlot(ameFit_k0$VC)
```
